### 2012-12-17 annualreports/2011/balancesheet.tex
Fixed 2011 annual report

\begin{center}
\begin{tabular}{  l  r  r r r}
\toprule
                            & \multicolumn{2}{c}{2011} &  \multicolumn{2}{c}{2010} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
                                                & £      & £     & £     & £     \\
{\bf Fixed Assets}                              &        &       &       &       \\
{\bf Tangible fixed assets}                     &        & 5,525 &       & 1,040 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Current Assets}                            &        &       &       &       \\
Rental Deposit                                  & 7,696  &       &       &       \\
Cash at bank and in hand                        & 7,688  &       & 8,642 &       \\
Creditors: amounts falling due within one year  & -2,511 &       & -1,343&      \\
Prepaid Subscriptions                           & -610   &       &       &      \\
{\bf Net current assets}                        &        & 20,908 &       & 7,285 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Total assets less current liabilities}     &        & 17,787 &       & 8,339 \\
\cmidrule(r){2-3} \cmidrule(r){4-5}  \\
{\bf Capital and Reserves}&\\
Income and expenditure account                  &        & 10,267 &       & 8,339 \\
\bottomrule
\end{tabular}

@@

Approved by the Board for issue on the 28\superscript{th} of December 2011
\vspace{48pt}

>>>>

\begin{center}
\begin{tabular}{  l  r  r r r}
\toprule
                            & \multicolumn{2}{c}{2011} &  \multicolumn{2}{c}{2010} \\
\cmidrule(r){2-3} \cmidrule(r){4-5}
                                                & £      & £     & £     & £     \\
{\bf Fixed Assets}                              &        &       &       &       \\
{\bf Tangible fixed assets}                     &        & 5,525 &       & 1,040 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Current Assets}                            &        &       &       &       \\
Rental Deposit                                  & 7,696  &       &       &       \\
Cash at bank and in hand                        & 7,688  &       & 8,642 &       \\
Creditors: amounts falling due within one year  & -2,511 &       & -1,343&      \\
Prepaid Subscriptions                           & -610   &       &       &      \\
{\bf Net current assets}                        &        & 12,263 &       & 7,299 \\
\cmidrule(r){2-3} \cmidrule(r){4-5} \\
{\bf Total assets less current liabilities}     &        & 17,787 &       & 8,339 \\
\cmidrule(r){2-3} \cmidrule(r){4-5}  \\
{\bf Capital and Reserves}&\\
Income and expenditure account                  &        & 17,787 &       & 8,339 \\
\bottomrule
\end{tabular}

@@

Approved by the Board for issue on the 22\superscript{nd} of January 2012
\vspace{48pt}
